---
title: "Codebook for 'meandromeda'"
output: pdf_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

get_value_table <- function(var) {

  labs <- labelled::val_labels(var)

  if (!is.null(labs)) {
    val_labels <- tibble::enframe(labs, "Label", "Value")
  } else {
    val_labels <- tibble::tibble(values = sort(unique(var)))
  }

  val_labels %>%
    dplyr::full_join(table(var, useNA = "ifany") %>%
                       tibble::enframe("Value", "n") %>%
                       dplyr::mutate_all(as.integer),
                     by = "Value") %>%
    dplyr::select("Value", "Label", "n") %>%
    dplyr::mutate(Label = ifelse(is.na(.data$Label), "Missing", .data$Label))
}

library(magrittr)
```

```{r}
data <- readRDS('data.rds')
```

# Project information
* Subjects = `r nrow(data)`
* Variables = `r ncol(data)`
* Started: `r min(data$STARTED)`
* Ended: `r max(data$STARTED)`

# Variable information

## [SD07] Purchasing intentions

* Question wording: %game% will be released on March 21 in the US and on March 23 in Europe. Which of the following statements best describes your intentions in relation to purchasing/playing %game%?

* Type: nominal
* Input: selection
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD07), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_01] Motives: ... slip into different roles.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_02] Motives: ... do things that are impossible or difficult in real life.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_03] Motives: ... achieve better and better results.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_04] Motives: ... enhance my in-game skills by training.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_05] Motives: ... explore and investigate the game world.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_06] Motives: ... be amazed by vast and „epic“ game content.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_07] Motives: ... experience game content that causes me to think about games in new ways.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_07), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_08] Motives: ... experience game content that stands out of my typical gaming experience.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_08), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_09] Motives: ... make friends.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_09), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_10] Motives: ... get to know other players.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_10), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_11] Motives: ... conjointly play with others.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_11), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_12] Motives: ... play with others in a team.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_12), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_13] Motives: ... beat my co-players.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_13), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS01_14] Motives: ... compare my performance with others.

* Question wording: People play games for many different reasons. We would like to know why you want to play %game%.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS01_14), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS02_01] Attributes: Graphics

* Question wording: And how important are the following aspects of %game% to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS02_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS02_02] Attributes: Mechanics / controls

* Question wording: And how important are the following aspects of %game% to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS02_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS02_03] Attributes: Topic of the game

* Question wording: And how important are the following aspects of %game% to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS02_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS02_04] Attributes: Story of the game

* Question wording: And how important are the following aspects of %game% to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS02_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GS02_05] Attributes: Game world

* Question wording: And how important are the following aspects of %game% to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GS02_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_01] BFI-10: ... is reserved. (reversed)

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_02] BFI-10: ... is generally trusting.

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_03] BFI-10: ... tends to be lazy. (reversed)

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_04] BFI-10: ... is relaxed, handles stress well. (reversed)

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_05] BFI-10: ... has few artistic interests. (reversed)

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_06] BFI-10: ... is outgoing, sociable.

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_07] BFI-10: ... tends to find fault with others. (reversed)

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_07), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_08] BFI-10: ... does a thorough job.

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_08), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_09] BFI-10: ... gets nervous easily.

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_09), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE01_10] BFI-10: ... has an active imagination.

* Question wording: How well do the following statements describe your personality?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE01_10), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_01] Eudaimonic and hedonic motivations: I like games that challenge my way of seeing the world.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_02] Eudaimonic and hedonic motivations: I like games that make me more reflective.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_03] Eudaimonic and hedonic motivations: I like games that focus on meaningful human conditions.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_04] Eudaimonic and hedonic motivations: My favorite kinds of games are ones that make me think.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_05] Eudaimonic and hedonic motivations: I am very moved by games that are about people’s search for greater understanding in life.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_06] Eudaimonic and hedonic motivations: I like games that have profound meanings or messages to convey.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_07] Eudaimonic and hedonic motivations: It’s important to me that I have fun when playing a game.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_07), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_08] Eudaimonic and hedonic motivations: Games that are enjoyable are among my favorites.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_08), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_09] Eudaimonic and hedonic motivations: I find that even simple games can be enjoyable as long as they are fun.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_09), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_10] Eudaimonic and hedonic motivations: I like games that may be considered "silly" or "shallow" if they let me have a good time.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_10), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_11] Eudaimonic and hedonic motivations: For me, the best games are ones that are entertaining.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_11), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE02_12] Eudaimonic and hedonic motivations: My favorite kinds of games are joyful and fun.

* Question wording: People play video games for different reasons. When you think about the <span style="color: #5273B9;">games you like in general</span>, how well do the following statements reflect your gaming preferences?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE02_12), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE03_01] Awe: I often feel awe.

* Question wording: When thinking about yourself: How strongly do you agree with the following statements?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE03_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE03_02] Awe: I see beauty all around me.

* Question wording: When thinking about yourself: How strongly do you agree with the following statements?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE03_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE03_03] Awe: I feel wonder almost every day.

* Question wording: When thinking about yourself: How strongly do you agree with the following statements?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE03_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE03_04] Awe: I often look for patterns in the objects around me.

* Question wording: When thinking about yourself: How strongly do you agree with the following statements?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE03_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE03_05] Awe: I have many opportunities to see the beauty of nature.

* Question wording: When thinking about yourself: How strongly do you agree with the following statements?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE03_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [PE03_06] Awe: I seek out experiences that challenge my understanding of the world.

* Question wording: When thinking about yourself: How strongly do you agree with the following statements?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$PE03_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD01_01] Age: I am ... years old.

* Question wording: How old are you?
* Type: metric
* Input: open
* System name: NA

## [SD02] Gender

* Question wording: What is your gender?
* Type: nominal
* Input: selection
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD03] Education

* Question wording: What is the highest level of education you have completed?
* Type: nominal
* Input: selection
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD04_01] Gaming per weekday:  ... minutes on each week day.

* Question wording: How many minutes do you spend on average on a <em>week day</em> (Monday – Friday) playing video games?
* Type: metric
* Input: open
* System name: NA

## [SD05_01] Gaming per weekend day:  ... minutes each weekend day.

* Question wording: And how many minutes do you spend on average on a <em>weekend day</em> (Saturday and Sunday) playing video games?

* Type: metric
* Input: open
* System name: NA

## [SD06] Familiarity series

* Question wording: As you may know, %game% is not the first title in the %gameShort% series. Hence, first of all, we would like to know how familiar you are with the game series.
* Type: nominal
* Input: selection
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD08_01] Remarks: [01]

* Question wording: 
* Type: text
* Input: open
* System name: NA

## [SD09] Language profiency

* Question wording: How experienced are you with the English language?
* Type: nominal
* Input: selection
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD09), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD10] Nationality

* Question wording: What country are you from?
* Type: nominal
* Input: selection
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD10), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD10s] Nationality (free text)

* Question wording: What country are you from?
* Type: text
* Input: open
* System name: NA

## [SD12_01] Fandom: I consider myself to be a %gameShort% fan.

* Question wording: When you think of the %gameShort% franchise in general, how much do the following statements apply to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD12_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD12_02] Fandom: My friends see me as a %gameShort% fan.

* Question wording: When you think of the %gameShort% franchise in general, how much do the following statements apply to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD12_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD12_03] Fandom: I have spend a considerable amount of money on %gameShort% in the past years.

* Question wording: When you think of the %gameShort% franchise in general, how much do the following statements apply to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD12_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD12_04] Fandom: I have not devoted much energy to %gameShort% in the past years.

* Question wording: When you think of the %gameShort% franchise in general, how much do the following statements apply to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD12_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD12_05] Fandom: I followed or participated in discussions of the %gameShort% community in the past years (e.g., on Reddit or Facebook).

* Question wording: When you think of the %gameShort% franchise in general, how much do the following statements apply to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD12_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD12_06] Fandom: I have created %gameShort% related fan content myself in the past years (e.g., fan art, fanfiction, fansites, videos, walkthroughs).

* Question wording: When you think of the %gameShort% franchise in general, how much do the following statements apply to you?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$SD12_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_01] Gratifications obtained: I slipped into different roles.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_02] Gratifications obtained: I did things that are impossible or difficult in real life.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_03] Gratifications obtained: I achieved better and better results.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_04] Gratifications obtained: I enhanced my in-game skills by training.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_05] Gratifications obtained: I explored and investigated the game world.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_06] Gratifications obtained: I was amazed by vast and „epic“ game content.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_07] Gratifications obtained: I experienced game content that causes me to think about games in new ways.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_07), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_08] Gratifications obtained: I experienced game content that stands out of my typical gaming experience.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_08), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_09] Gratifications obtained: I made friends.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_09), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_10] Gratifications obtained: I got to know other players.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_10), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_11] Gratifications obtained: I conjointly played with others.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_11), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_12] Gratifications obtained: I played with others in a team.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_12), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_13] Gratifications obtained: I beat my co-players.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_13), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_14] Gratifications obtained: I compared my performance with others.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_14), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_15] Gratifications obtained: I liked the graphics of %game%.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_15), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_16] Gratifications obtained: I liked the mechanics/controls of %game%.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_16), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_17] Gratifications obtained: I liked the topic of %game%.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_17), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_18] Gratifications obtained: I liked the story of %game%.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_18), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE01_19] Gratifications obtained: I liked the game world of %game%.

* Question wording: Thanks! Now we are interested in your experience with %game% in greater detail. How do the following statements describe your playing experience with %game% so far?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE01_19), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_01] Eudaimonic and hedonic gratifications: I had a good time playing this game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_02] Eudaimonic and hedonic gratifications: I liked to play the game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_03] Eudaimonic and hedonic gratifications: I found the game entertaining.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_04] Eudaimonic and hedonic gratifications: It was great fun to take control in the game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_05] Eudaimonic and hedonic gratifications: The game invited me to take control of it.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_06] Eudaimonic and hedonic gratifications: The game was not at all interesting to me.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_07] Eudaimonic and hedonic gratifications: I found the game boring.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_07), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_08] Eudaimonic and hedonic gratifications: I was motivated to participate in this game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_08), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_09] Eudaimonic and hedonic gratifications: I found this game to be very meaningful.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_09), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_10] Eudaimonic and hedonic gratifications: I was moved by this game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_10), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_11] Eudaimonic and hedonic gratifications: The game was thought provoking.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_11), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_12] Eudaimonic and hedonic gratifications: I was at the edge of my seat while playing this game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_12), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_13] Eudaimonic and hedonic gratifications: This was a heart-pounding kind of game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_13), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_14] Eudaimonic and hedonic gratifications: The game was suspenseful.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_14), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_15] Eudaimonic and hedonic gratifications: I found the relationships I formed with the characters in this game fulfilling.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_15), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_16] Eudaimonic and hedonic gratifications: I really felt for the characters in the game.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_16), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE02_17] Eudaimonic and hedonic gratifications: It was hard for me to build an emotional connection to the characters.

* Question wording: Again, please think about your experience with %game% and tell us how much the following statements apply to you.
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE02_17), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_01] Affective reactions: ...upbeat

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_02] Affective reactions: ...happy

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_03] Affective reactions: ...sad

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_04] Affective reactions: ...depressed

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_04), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_05] Affective reactions: ...compassionate

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_05), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_06] Affective reactions: ...inspired

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_06), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_07] Affective reactions: ...introspective

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_07), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_08] Affective reactions: ...contemplative

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_08), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_09] Affective reactions: ...in awe

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_09), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_10] Affective reactions: ...in wonder

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_10), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_11] Affective reactions: ...amazed

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_11), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE03_12] Affective reactions: ...fascinated

* Question wording: People can experience several different feelings while playing a game. We would like to know how intensely you have experienced the following feelings while playing %game%. 

* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GE03_12), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GE05_01] Rating: [No Description] 01

* Question wording: The following questions deal with your experiences with %game%. Let's start with an overall rating: How would you rate %game% on a scale from 0 to 100 %? 
* Type: metric
* Input: scale
* System name: NA

## [GP01] Progress

* Question wording: How intensively have you played %game%? 
* Type: nominal
* Input: selection
* System name: NA

```{r}
knitr::kable(get_value_table(data$GP01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GP02_01] Play Time:  ... hours

* Question wording: How much time did you invest in playing %game% up to this point?
* Type: metric
* Input: open
* System name: NA

## [GP03_01] Continuance intentions: In the future, I will continue to play %game%.

* Question wording: And what about the future? How likely are you to continue to play and recommend %game%?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GP03_01), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GP03_02] Continuance intentions: In the future, I will play %game% often.

* Question wording: And what about the future? How likely are you to continue to play and recommend %game%?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GP03_02), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [GP03_03] Continuance intentions: I will recommend %game% to other people.

* Question wording: And what about the future? How likely are you to continue to play and recommend %game%?
* Type: ordinal
* Input: scale
* System name: NA

```{r}
knitr::kable(get_value_table(data$GP03_03), caption = 'Value labels & counts', align = c('l', 'l', 'r'))
```

## [SD11_01] Remarks W2: [01]

* Question wording: If you have any further questions or remarks, you may enter them here. 
* Type: text
* Input: open
* System name: NA

## [GP04_01] Restrictions: I finished the main story of %game%.

* Question wording: You have indicated that it is very unlikely that you will continue to play %game%. While we have already asked you about your enjoyment of the game, there are several other reasons why one does abandon a certain game. Please check all that apply to you.
* Type: dichotomous
* Input: checkbox
* System name: NA

## [GP04_02] Restrictions: %game% is too difficult for me.

* Question wording: You have indicated that it is very unlikely that you will continue to play %game%. While we have already asked you about your enjoyment of the game, there are several other reasons why one does abandon a certain game. Please check all that apply to you.
* Type: dichotomous
* Input: checkbox
* System name: NA

## [GP04_03] Restrictions: I do not have enough free time at the moment to play %game%.

* Question wording: You have indicated that it is very unlikely that you will continue to play %game%. While we have already asked you about your enjoyment of the game, there are several other reasons why one does abandon a certain game. Please check all that apply to you.
* Type: dichotomous
* Input: checkbox
* System name: NA

## [GP04_04] Restrictions: I have no more access to %game% (e.g., due to borrowing it).

* Question wording: You have indicated that it is very unlikely that you will continue to play %game%. While we have already asked you about your enjoyment of the game, there are several other reasons why one does abandon a certain game. Please check all that apply to you.
* Type: dichotomous
* Input: checkbox
* System name: NA

## [GP04_05] Restrictions: Other reason(s)

* Question wording: You have indicated that it is very unlikely that you will continue to play %game%. While we have already asked you about your enjoyment of the game, there are several other reasons why one does abandon a certain game. Please check all that apply to you.
* Type: dichotomous
* Input: checkbox
* System name: NA

## [GP04_05a] Restrictions: Other reason(s) (free text)

* Question wording: You have indicated that it is very unlikely that you will continue to play %game%. While we have already asked you about your enjoyment of the game, there are several other reasons why one does abandon a certain game. Please check all that apply to you.
* Type: text
* Input: open
* System name: NA
